\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-22 paper.tex
added architecture diagram to evaluation

>>>>

In this section we discuss a prototype implementation and evaluate its
performance. We first present the architecture of this implementation and
consider the impact it has from a development point of view. Next we use this
implementation to quantify its merits using a side-by-side comparison of
generated code versus a manual implementation.

\subsection{Architecture}

Figure \ref{fig:architecture} shows the architecture of the implementation.

\begin{figure}[ht]
  \centering
  \scalebox{.85}{
\begin{tikzpicture}[
  node distance=10mm and 20mm,
  ,>=stealth,thick,black!50,text=black,
  every new ->/.style={shorten >=1pt},
]
  \node (dsl)      [user,align=center]                                     {DSL};
  \node (code)     [generated,right=of dsl]                                {code};
  \node (image)    [generated,right=of code]                               {image};

  \node (nodes)    [dom,above right=of dsl,xshift=-20mm]                   {Nodes};
  \node (platform) [platform,below right=of dsl,align=center,xshift=-20mm] {Platform \&\\Language};
  \node (lib)      [native,below right=of code,align=center,xshift=-20mm]  {Software\\Library};

  \draw [->] (dsl)  -> (code)  node [midway,above=2pt] {generation};
  \draw [->] (code) -> (image) node [midway,above=2pt] {compilation};

  \draw [->,dashed] (nodes.south)    -> ++(0,-15mm);
  \draw [->,dashed] (platform.north) -> ++(0,15mm);
  \draw [->,dashed] (lib.north)      -> ++(0,15mm);
\end{tikzpicture}
}
  \caption{Architecture of Prototype Implementation}
  \label{fig:architecture}
\end{figure}

\subsection{Implementation}
